%------------------------------------------------------------------------------------------------------------
%------------------------------------------------- Publicaciones --------------------------------------------
\chapter*{Publicaciones}
Durante el desarrollo de esta tesis se han generado diversas publicaciones. Las principales se detallan a continuaci{\'o}n:
\begin{enumerate}
\small
    \item[A-] \textbf{An Approach to Improve the Performance of Adaptive Predictive Control Systems: Theory,  Simulations and Experiments.} M.
        Jord{\'a}n, M. Basualdo and D. Zumoffen. \textit{International Journal
    Of Control}. 2006, 79(10), 1216/1236.
    \item[B-] \textbf{Robust Adaptive Predictive Fault-Tolerant Control Linked with Fault Diagnosis System Applied On a Nonlinear Chemical Process.} D.
        Zumoffen, M. Basualdo, M. Jord{\'a}n and A. Ceccatto.
    \textit{Proceedings of the 45th IEEE Conference on Decision and Control}. 2006, 3512/3517. San Diego,
    CA, USA.
    \item[C-] \textbf{Robust Adaptive Predictive Fault-Tolerant Control Integrated To a Fault-Detection System Applied to a Nonlinear Chemical
        Process.} D. Zumoffen, M. Basualdo, M. Jord{\'a}n and A.
    Ceccatto. \textit{Ind. Eng.
    Chem. Res.}. 2007, 46(22), 7152/7163.
    \item[D-] \textbf{From Large Chemical Plant Data to Fault Diagnosis Integrated to Decentralized Fault-Tolerant Control: Pulp Mill Process
        Application.} D. Zumoffen and M. Basualdo. \textit{Ind. Eng.
    Chem. Res.}. 2008, 47(4), 1201/1220.
    \item[E-] \textbf{Improvements in Fault Tolerance Characteristics for Large Chemical Plants Part I: Waste Water Treatment Plant with Decentralized
        Control}. D. Zumoffen and M. Basualdo. \textit{Ind. Eng. Chem. Res.}. 2008, 47(15), 5464/5481.
    \item[F-] \textbf{Improvements in Fault Tolerance Characteristics for Large Chemical Plants Part II: Pulp Mill Process with Model Predictive Control.} D.
        Zumoffen, M. Basualdo and G. Molina. \textit{Ind. Eng. Chem. Res.}. 2008, 47(15), 5482/5500.
\end{enumerate}
\normalsize

Las publicaciones A, B y C forman parte del cap{\'\i}tulo 3 y la estructura fundamental del cap{\'\i}tulo 4. A su vez las publicaciones D, E y F estructuran el
cap{\'\i}tulo 5. En cada caso, dichos cap{\'\i}tulos pretenden otorgar un visi{\'o}n extendida de las publicaciones documentando nuevos resultados y estrategias.

Adem{\'a}s, numerosos trabajos interdiciplinarios se han llevado a cabo en este per{\'\i}odo. El resultado de dicha interacci{\'o}n se ve reflejada en las
publicaciones enunciadas anteriormente y los siguientes trabajos presentados en congresos y reuniones cient{\'\i}ficas:
\begin{enumerate}
\small \item \textit{Desarrollo De Un Sensor Virtual De Composiciones Para La Implementaci{\'o}n De Control
 Con Trayectoria {\'O}ptima Aplicado A Destilaci{\'o}n Batch.} J.P. Ruiz, F. Garetto, D. Zumoffen y M.
 Basualdo. Congreso X RPIC, Argentina. 2003.

\item \textit{A Nonlinear Soft Sensor For Quality Estimation And Optimal Control Applied In A Ternary Batch Distillation Column.} J.P. Ruiz, D.
Zumoffen, M. Basualdo and L. Jimenez  Esteller. ESCAPE 14 European Symposium on Computer Aided Process Engineering, Portugal. 2004.

\item \textit{Aplicaci{\'o}n De Control Predictivo Funcional Para El Seguimiento De Una Trayectoria {\'O}ptima De Temperatura En Una Columna De Destilaci{\'o}n
Batch Multicomponente.} D. Zumoffen, L. Garyulo y M. Basualdo. XIX Congreso Argentino de Control Autom{\'a}tico, Argentina. 2004.

\item \textit{Predictive Functional Control Applied To Multicomponent Batch Distillation Column.} D. Zumoffen, L. Garyulo, M. Basualdo and L.
Jim{\'e}nez. ESCAPE 15, European Symposium on Computer Aided Process Engineering, Spain. 2005, 1465/1470.

\item \textit{Sistema De Detecci{\'o}n De Fallas En Un CSTR Controlado Con PFC.} D. Zumoffen, M. Basualdo y A. Ceccatto. Congreso XI RPIC, Argentina.
2005.

\item \textit{Control Tolerante Predictivo Funcional aplicado A Un CSTR.} D. Zumoffen, M. Basualdo y M. Jord{\'a}n. Congreso XI RPIC, Argentina. 2005.

\item \textit{Control predictivo generalizado no lineal aplicado a una columna de destilaci{\'o}n batch ternaria.} J. Walczuk, L. Caviglia, D. Zumoffen y
M. Basualdo. Congreso XI RPIC, Argentina. 2005.

\item \textit{On the Design of Fault-Tolerant Systems using Robustness Filtering with Adaptive Control.} M. Jord{\'a}n, M. Basualdo and D. Zumoffen.
Congreso XI RPIC, Argentina. 2005.

\item \textit{An Industrial Application Of Signal Processing For Developing A Fault Diagnosis System Linked With A Fault Tolerant Control Strategy.}
M. Basualdo and D. Zumoffen. Workshop on Signal Processing (WSP06), Argentina. 2006.

\item \textit{Control Tolerante A Fallos Integrado A Un Sitema De Diagnosis Basado En An{\'a}lisis De Principales Componentes Y L{\'o}gica Difusa.} D.
Zumoffen, M. Basualdo y G. Molina. XX  Congreso Argentino de Control Autom{\'a}tico, Argentina. 2006.

\item \textit{Fault Detection and Estimation System Integrated To Fault Tolerant Control. Part I: FDIE System Design.} D. Zumoffen and M. Basualdo.
Congreso XII RPIC, Argentina. 2007.

\item \textit{Fault Detection and Estimation System Integrated To Fault Tolerant Control. Part II: Reconfiguration of the Control Strategy.} D.
Zumoffen and M. Basualdo. Congreso XII RPIC, Argentina. 2007.

\item \textit{Hybrid Fault Diagnosis For Large Chemical Plants Under Control.} D. Zumoffen and M. Basualdo. ESCAPE 18, European Symposium on Computer
Aided Process Engineering, France. 2008.

\item \textit{Fault Diagnosis and Identification System Applied to a Non-invasive Biosensor of Blood Glucose.} M. Basualdo, D. Zumoffen and A.
Rigalli. ESCAPE 18, European Symposium on Computer Aided Process Engineering, France. 2008.

\item \textit{Monitoreo Y CTF en Grandes Plantas Qu{\'\i}micas. Parte I: Dise{\~n}o del SDDEF.} D. Zumoffen y M. Basualdo. XXI Congreso Argentino de Control
Autom{\'a}tico, Buenos Aires, Argentina. 2008.

\item \textit{Monitoreo Y CTF en Grandes Plantas Qu{\'\i}micas. Parte II: Integraci{\'o}n al CTF.} D. Zumoffen y M. Basualdo. XXI Congreso Argentino de
Control Autom{\'a}tico, Buenos Aires, Argentina. 2008.
\end{enumerate}
\normalsize
